The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2022-01-05 paper.tex
update

\begin{abstract}
\begin{enumerate}
  \item Release the caveat of jet direction.
  \item Rule out the hadronic process.
  \item Predict the small inner bubbles.
  \item How to explain why we assume e\_CR << e\_gas
  \item How to explain the lifespan of bubbles is too long.
  \item How to explain the jet power.
  \item How to explain the inconsistant of gamma-ray map.
\end{enumerate}
\end{abstract}

@@

\section{to-do-list}
\begin{enumerate}
  \item Predict cold inner bubbles, emitting OIII or OII spectrum.
\end{enumerate}

>>>>

\begin{abstract}
\end{abstract}

@@
